Robust self-testing of large entanglement with constant-sized correlations

### 2019-04-29 Draft/draft.tex
Added comments to section 2 of the draft

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we are interested in is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
We denote a Hilbert space by $\calH$. Note that we only work with finite Hilbert spaces in this work.
When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
$\calH_B$.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
the maximally entangled state is denoted by 
\begin{align}
	\ket{\EPR{2}} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are given by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}

@@

We use some basic number theory in our work. 
\begin{definition}
A primitive root of a prime number
$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
in the multiplicative group of integers modulo $d$, $\Zd$.
\end{definition}
In other words,
$r$ is the generator of $\Zd$.

@@

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
\carl{You need to put explicit labels on the quantum systems used by
Alice and Bob.  (Later on you seem to use ``$A$'' and ``$B$'' to refer to those systems, but those are also
the same letters you use for Alice's and Bob's measurements.  That's confusing.)}
\hf{Addressed in the notation part. --H.F}
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
\carl{Make this clear in the definition itself.}
\hf{I made the definition of the scoring function part of the big definition now.}
In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables.

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
the finite-dimensional representation of a finitely presented group
over $\Z_2$, which is called the solution group.
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,\uc) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a prefect strategy for 
the linear system game ($H\ux = \uc$) has
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$,
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.

%-------------------------------------------------------------------------------
\subsection{The weighted CHSH inequality \cite{acin2012}.}
%-------------------------------------------------------------------------------
The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
The input sets and output sets of Alice and Bob are
$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
The scoring function for the $\alpha$-weighted CHSH test is defined by
\begin{align}
	V(a,b,x,y)_{\alpha-CHSH} = 
	\begin{cases}
		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
	\end{cases}
\end{align}
Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
The weighted CHSH inequality states that 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
\end{align}
where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of of the observables. 
The weighted CHSH inequality is true 
If Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
However, If they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
strategy up to some local isometry, 
which is a phenomenon referred as a robust self-test.
We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.

\carl{Before the next definition, you should define what a ``correlation'' is.}
\hf{Done. I decided to remove the definition of self-testing here because I think it is hard
to give a general robust self-testing definition and it suffices to just give our robust self-testing result.}

\carl{Section 2 needs to be cleaned up in some places, but overall it is pretty good.}

%-----------------------------------------------------------
\subsection{Approximation tools}
%-----------------------------------------------------------
In the rest of the paper, we use the following approximation results implicitly and explicitly.
\begin{proposition}
	\label{prop:inner_pd}
	Let $\ket{v}$ and $\ket{v'}$ be vectors with length less than equal to $1$ satisfying the relation that $\ket{v} \appd{\epsilon} \ket{v'}$
	then for any unit vector $\ket{u}$,
	\begin{align}
		 \braket{v}{u} \appd{\ep} \braket{v'}{u} .
	\end{align}	
\end{proposition}
\begin{proof}
	We can write $\ket{v'} = \ket{v} + \ket{v''}$, where $\norm{\ket{v''}} \leq \epsilon$,
	then
	\begin{align}
	\norm{ \braket{v}{u} - \braket{v'}{u} } = \norm{\braket{v''}{u}} \leq \norm{\ket{u}}\norm{\ket{v''}} \leq \epsilon.
	\end{align}
\end{proof}
\begin{proposition}
	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with length less than equal to $1$
	such that 
	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$
	then 
	\begin{align}
		\braket{u_1}{u_2} \appd{\ep_1+ \ep_2} \braket{v_1}{v_2}.
	\end{align}
\end{proposition}
\begin{proof}
	By direct calculation we have
	\begin{align}
		\norm{ \braket{u_1}{u_2} - \braket{v_1}{v_2}} \leq &\norm{\braket{u_1}{u_2} - \braket{v_1}{u_2}}
		+ \norm{\braket{v_1}{u_2} - \braket{v_1}{v_2}} \\
		\leq & \ep_1 + \ep_2,
	\end{align}
	where we used \cref{prop:inner_pd}.
\end{proof}
\begin{proposition}
\label{prop:orthog}
	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with length less or equal to $1$,
	which satisfy the condition that 
	\begin{align}
		H\ket{u} \appd{\ep_1} a \ket{u}, \\
		H\ket{v} \appd{\ep_2} b \ket{v}, 
	\end{align}
	for some $a > b \in \R$, then
	\begin{align}
		\norm{\braket{u}{v}} \leq \frac{\ep_1+\ep_2}{a-b}.
	\end{align}
\end{proposition}
\begin{proof}
	We write $H\ket{u} = a\ket{u} + \ket{u'}$ such that $\norm{\ket{u'}} \leq \ep_1$.
	Similarly, we write $H\ket{v} = b\ket{v} + \ket{v'}$ such that $\norm{\ket{v'}} \leq \ep_2$.
	Then, we know
	\begin{align}
		\bra{v}H\ket{u} = a\braket{v}{u} + \braket{v}{u'},\\
		\bra{v}H\ket{u}  =b\braket{v}{u} + \braket{v'}{u},
	\end{align}
	Subtracting the second equation from the first equation gives us that 
	\begin{align}
		\norm{\braket{v}{u}} = \frac{\norm{\braket{v'}{u} -  \braket{v}{u'}}}{a-b} \leq \frac{\norm{\ket{v}}\norm{\ket{u'}}+
		\norm{\ket{u}}\norm{\ket{v'}}}{a-b} 
		\leq \frac{\ep_1+\ep_2}{a-b}.
	\end{align}
\end{proof}
\begin{proposition}
\label{prop:close_vec}
	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$ and
	$\norm{\ket{v}} \appd{\ep_2} 1$ , if $\braket{u}{v} \geq 1 - \ep_3$,
	then
	\begin{align}
		\ket{u} \appd{O(\sqrt{\ep_1+\ep_2+\ep_3})} \ket{v}.
	\end{align}
\end{proposition}
\begin{proof}
	Direct calculation gives us that
	\begin{align}
		\norm{\ket{u} - \ket{v}}^2 &= \norm{\ket{u}}^2 + \norm{\ket{v}}^2 - 2\braket{u}{v} \\
		&\leq (1+\ep_1)^2 + (1+\ep_2)^2 - 2(1 - \ep_3)\\
		&= 2(\ep_1+\ep_2+\ep_3)+ \ep_1^2 + \ep_2^2\\
		& = O(\ep_1+\ep_2+\ep_3).
	\end{align}
\end{proof}
\begin{proposition}
	Let $\ket{u}$ be a vector with length less or equal to $1$ such that for a unitary $U$,
	\begin{align}
		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C,
	\end{align}
	then
	\begin{align}
		U^n \ket{u} \appd{n\ep} a^n \ket{u} \text{ for all } n \geq 1.
	\end{align}
\end{proposition}
\begin{proof}
	We can prove it by induction. 
	For $n=1$, the statement is satisfied.
	Assume it holds for $n = k-1$ and consider $n = k$, then we have
	\begin{align}
		&\norm{U^k \ket{u} - a^k\ket{u}} \\
		\leq &\norm{U} \norm{U^{k-1} \ket{\psi} - a^{k-1}\ket{\psi}} + \norm{a^{k-1}}
		\norm{U\ket{\psi} - a \ket{\psi}}\\
		\leq &(k-1)\ep + \ep = k \ep,
	\end{align}
	where we used the fact that $\norm{U} = 1$ and $\norm{a} \leq 1$.
\end{proof}

>>>>

%========================================
\section{Preliminaries and notations}
\label{sec:prelim}
%========================================
%-----------------------------------
\subsection{Notations}
%-----------------------------------
The maximally entangled state of local dimension $d-1$ for some odd prime $d$ that we are interested in is denoted by
\begin{align}
\ket{\EPR{d-1}} = \frac{1}{\sqrt{d-1}} \sum_{j = 1}^{d-1} \ket{j}\ket{d-j}.
\end{align}
The superscript $(d-1)$ stresses the dimension of the local Hilbert space and we follow this convention through this paper.
We denote a Hilbert space by $\calH$.  \carl{That last sentence is too vague.  Does $\calH$ refer to a specific Hilbert space?}
Note that we only work with finite Hilbert spaces in this work.
When there are multiple Hilbert spaces, we label them with subscripts, for example, $\calH_A$ and
$\calH_B$.
The $d$-th root of unity is denoted by $\omega_d:=e^{2\pi i/d}$. In the qubit case, 
the maximally entangled state is denoted by 
\begin{align}
	\ket{\EPR{2}} = \frac{1}{\sqrt{2}}(\ket{00} + \ket{11}),
\end{align}
and the Pauli operators are given by
\begin{align}
	\paulix = \ketbra{0}{1}+\ketbra{1}{0} && \pauliz = \ketbra{0}{0} - \ketbra{1}{1}.
\end{align}

@@

We use some basic number theory in our work. 
\begin{definition}
A primitive root of a prime number
$d$ is \hf{the smallest integer} $r$ such that $r \pmod{d}$ has multiplicative order $d-1$
in the multiplicative group of integers modulo $d$, $\Zd$.  \carl{I'm skeptical about whether that's the standard definition.  (For example, the definition on wikipedia doesn't include that ``smallest integer'' part.)}
\end{definition}
In other words,
$r$ is the generator of $\Zd$.

@@

A quantum strategy of a nonlocal game presented in terms of projective measurements
consists of projective measurements $\{\{M_x^a\}_a\}_x$ on Alice's side, 
$\{\{N_y^b\}_b\}_y$ on Bob's side, and a shared state $\ket{\psi}$, where 
$(M_x^a)^2 = M_x^a = (M_x^a)^\dagger$ and $(N_y^b)^2 = N_y^b = (N_y^b)^\dagger$.
Then Alice and Bob's quantum strategy produces the conditional probability distribution
\begin{align}
	\pr{ab}{xy} = \bra{\psi} A_x^a \x B_y^b \ket{\psi} \text{ for all } (a,b,x,y) \in \calA \times \calB \times \calX \times \calY,
\end{align}
\carl{Check the use of notation above (``$A$'', ``$B$'').}
\begin{definition}
	Given sets $\calX, \calY, \calA, \calB$, a correlation is a collection of conditional probability distributions
	$\{\pr{ab}{xy}: a \in \calA, b \in \calB\}_{x \in \calX, y \in \calY}$.
\end{definition}
A particular type of nonlocal games that we are interested in is called linear system games, which is defined below.
\begin{definition}[Linear system game]
 Let $H\ux = \uc$ be an $m \times n$ system of linear equations over $\Z_2 = \{0, 1\}$,
 where $H$ is an $m$-by-$n$ matrix with entries in $\Z_2$ and 
 $\uc$ is a length-$n$ vector with entries in $\Z_2$. 
 The associated linear system game involves two
 players Alice and Bob, where Alice is given an equation number $i \in \calX = \{1 \dots m\}$ and replies with $\ua \in \calA = \Z_2^{\times n}$,
 and Bob is given a variable number $j \in \calY = \{1 \dots n\}$ and replies with an assignment $b \in \calB = \Z_2$. The 
 scoring function is defined by
 \begin{align}
 	V(\ua, b, i, j) =
	\begin{cases}
		1, \quad \text{if } \sum_{k= 1}^n H(i,k) \ua(k) \equiv c(i) \pmod 2 \text{ and } \ua(j) = b \\
		0,  \quad \text{otherwise.}
	\end{cases}
\end{align}
\end{definition}
In the later parts, we will work with quantum strategies for the linear system game presented in terms of binary observables.
\begin{definition}[Quantum strategy of a linear system game]
\label{def:q_strat}
A quantum strategy presented in terms of binary observables for the linear system game $(H\ux = \uc)$ consists of 
\begin{enumerate}
	\item a pair of finite Hilbert spaces $\calH_A$ and $\calH_B$;  \carl{``finite-dimensional''?}
	\item a collection of binary observables $B_j$, $1 \leq j \leq n$, on $\calH_B$
	such that $B_j^2 = \1$ for every $1 \leq j \leq n$;  \carl{You're using ``$A$,$B$'' here still.}
	\item a collection of binary observables $A_{ij}$, $1\leq i \leq m$, $1\leq j\leq n$ 
	on $\calH_A$ such that 
	\begin{enumerate}
		\item $A_{ij}^2 = \1$ for every $i,j$,
		\item $\Pi_j A_{ij}^{H(i,j)} = (-\1)^{\uc(i)}$ for every $i$, and
		\item $A_{il}A_{ik} = A_{ik}A_{il}$ for every $i$ and $H(i,l) = H(i,k) =1$;
	\end{enumerate} 
	and
	\item a quantum state $\ket{\psi} \in \calH_A \x \calH_B$.
\end{enumerate}
\end{definition}
Note that any quantum strategy presented in terms of binary observables can be 
converted to a quantum strategy presented in terms of projective measurement by looking into
the spectral decompositions of the observables.  \carl{If you're going to make that claim, you should make it more precise.  Add a sentence explaining briefly how the construction is done.}

%It has been shown in Ref.~\cite{cleve2014} that the linear system game has a perfect strategy 
%satisfying conditions in \cref{def:q_strat} if and only if the linear system has a finite-dimensional
%operator solution in the following sense.  \carl{There's a missing reference here?}
%\begin{definition}[Operator solution of a linear system]
%\label{def:op_sol}
%	An operator solution to a linear system $Hx =c$ over $\Z_2$ is a sequence of \hf{finite-dimensional} Hermitian 
%	operators \hf{with finite entries}: $A_1, A_2, \dots A_n$ on a Hilbert space $\calH$ such that \carl{(What does the word ``bounded'' mean here?  It might
%	be best to just state the definition for finite dimensions only.)}
%	\begin{enumerate}
%		\item $A_i^2 = \1$, i.e. $A_i$ is a binary observable, for all $1 \leq i \leq n$;
%		\item If $x_l$ and $x_k$ appear in the same equation, then $A_l$ and $A_k$ commute;
%		\item for all $1 \leq i \leq m$,
%		\begin{align*}
%			\Pi_{k=1}^n A_k^{H(i,k)} = (-1)^{c(i)}\1.
%		\end{align*}
%	\end{enumerate}
%	A finite dimensional operator solution to a linear system $Hx = c$ over $\Z_2$ is an operator
%	solution in which the Hilbert space is finite-dimensional.
%\end{definition}
%Perfect quantum strategies can be extracted from operator solutions and vice versa.
A quantum strategy using binary observables for the linear system game associated with $H\ux = \uc$ can be constructed from
the finite-dimensional representation of a finitely presented group
over $\Z_2$, which is called the solution group.  \carl{The phrase ``the finite-dimensional
representation'' is confusing -- it sound like you are implying that there is only one representation.}
\begin{definition}[Solution group of a linear system game]
	\label{def:presentation}
	Let $H\ux = \uc$ be an $m \times n$  linear system. The solution group of this system
	is the group
	\begin{align*}
		\Gamma(H,\uc) := \ip{
		x_1,\dots x_n, J: &J^2 = x_i^2 = e, Jx_i = x_iJ \text{ for all }1 \leq i \leq n, \\
				& \Pi_{j=1}^n x_j^{H(i,j)} = J^{\uc(i)} \text{ for all } 1 \leq i \leq m, \text{ and } \\
				& x_l x_k = x_k x_l \text{ if } H(i,k) = H(i,l) = 1 \text{ for some } i
				} .
	\end{align*}
\end{definition}
We remark that a linear system game can be extracted from a solution group and \textit{vice versa}.
Let $\Psi$ be a finite-dimensional representation of $\Gamma(H,\uc)$ such that $\Psi(J) = -\1$ on the vector space $\C^d$, then a perfect strategy for 
the linear system game ($H\ux = \uc$) has \carl{Replace ``has'' with ``is given by''.}
\begin{enumerate}
	\item $A_{ij} = \Psi(x_j)$ for all $ 1 \leq i \leq m$ and $1 \leq j \leq n$,
	\item $B_j = \Psi(x_j)$ for all $1 \leq j \leq n$, \carl{Do you need a transpose symbol in here somewhere?}
	\item the maximally entangled state $\ket{\psi} = \frac{1}{\sd} \sum_{k=1}^d \ket{k}\ket{k}$.
\end{enumerate}
We follow a similar approach to construct our ideal strategy. \carl{I don't think the reader will know what ``ideal strategy'' refers to at this point.}. However, our strategy uses a different maximally entangled state,
so we justify our strategy more carefully.
For concepts related to group presentations, we refer to Sec.~$2$ of Ref.~\cite{slofstra2017}.
For concepts related to group representations, we refer to Sec.~$2.5$ of Ref.~\cite{coladan2017}.  \carl{These last two sentences seem out of place -- consider rephrasing and relocating.}

%-------------------------------------------------------------------------------
\subsection{The weighted CHSH inequality \cite{acin2012}.}
%-------------------------------------------------------------------------------
The weighted CHSH inequality is extracted from the CHSH test, which is another nonlocal game. 
The input sets and output sets of Alice and Bob are
$\calX = \calY = \{1, 2\}$ and $\calA = \calB = \Z_2$.
The scoring function for the $\alpha$-weighted CHSH test is defined by
\begin{align}
	V(a,b,x,y)_{\alpha-CHSH} = 
	\begin{cases}
		\alpha (-1)^{a + b}, \quad \text{if } x = 1 \\
		(-1)^{a + b}, \quad \text{if } x = 2,\; y =1 \\
		(-1)^{1 + a + b}, \quad \text{if } x = y =2.
	\end{cases}
\end{align}
\carl{What is the input distribution?}
Let Alice and Bob's quantum strategy in terms of projectors be $( \{\{M_x^a\}_a\}_x, \{\{N_y^b\}_b\}_y, \ket{\psi})$. 
We define binary observables $M_x := M_x^0 - M_x^1$ and $N_y := N_y^0 - N_y^1$ from Alice and Bob's projectors.
The weighted CHSH inequality states that 
\begin{align}
	\label{eq:chsh_op}
	\ip{\I_\alpha} = \alpha\ip{M_1N_1}+\alpha\ip{M_1N_2} + \ip{M_2N_1} - \ip{M_2N_2}\leq 2\alpha,
\end{align}
where $\ip{M_xN_y} := \bra{\psi} M_xN _y \ket{\psi}$ is the expectation value of the observables. 
The weighted CHSH inequality is true 
if Alice and Bob share product state $\ket{\phi} = \ket{\phi_A} \x \ket{\phi_B}$.
However, if they share an entangled state $\ket{\psi}$, the value of $\ip{\I_\alpha}$ can be as large as
\begin{align}
\label{eq:chsh_max}
 \ip{\I_\alpha}_{\max} = 2\sqrt{1+\alpha^2}.
\end{align}
\carl{You need to cite the results that you're summarizing here (or refer to an appendix).}
\begin{definition}[Ideal strategy to achieve $\ip{\I_\alpha}_{\max}$]
	\label{def:ideal}
	Define $\mu = \arctan(1/\alpha)$.
	The ideal strategy for weighted CHSH with parameter $\alpha$, which achieves the value $\ip{\I_\alpha}_{\max}$, 
	consists of the joint state $\ket{\EPR{2}}$ and observables $\tM_1 = \pauliz$, $\tM_2 = \paulix$,
	$\tN_1 = \cos(\mu) \pauliz+ \sin(\mu) \paulix$ and $\tN_2 = \cos(\mu) \pauliz - \sin(\mu) \paulix$.
\end{definition}
An interesting observation of the weighted CHSH inequality is that if some strategy can achieve 
value $\ip{\I_\alpha}$ close to $\ip{\I_\alpha}_{\max}$, then the strategy is close to the ideal 
strategy up to some local isometry, 
which is a phenomenon referred as a robust self-test.
We give the formal statement of this self-testing property of $\ip{\I_\alpha}_{\max}$ in \cref{sec:chsh}.

%-----------------------------------------------------------
\subsection{Approximation tools}
%-----------------------------------------------------------
In the rest of the paper, we use the following approximation results implicitly and explicitly.
	\label{prop:inner_pd}
	Let $\ket{v}$ and $\ket{v'}$ be vectors with length less than equal to $1$ satisfying the relation that $\ket{v} \appd{\epsilon} \ket{v'}$
	then for any unit vector $\ket{u}$,
		 \braket{v}{u} \appd{\ep} \braket{v'}{u} .
	\carl{Check the grammar in this proposition.}
	We can write $\ket{v'} = \ket{v} + \ket{v''}$, where $\norm{\ket{v''}} \leq \epsilon$,
	\norm{ \braket{v}{u} - \braket{v'}{u} } = \norm{\braket{v''}{u}} \leq \norm{\ket{u}}\norm{\ket{v''}} \leq \epsilon.
\carl{Question: Do we actually need the assumption that $v,v'$ have length less than $1$?}
	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with length less than equal to $1$
	such that 
	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$
		\braket{u_1}{u_2} \appd{\ep_1+ \ep_2} \braket{v_1}{v_2}.
	By direct calculation we have
		\norm{ \braket{u_1}{u_2} - \braket{v_1}{v_2}} \leq &\norm{\braket{u_1}{u_2} - \braket{v_1}{u_2}}
		+ \norm{\braket{v_1}{u_2} - \braket{v_1}{v_2}} \\
		\leq & \ep_1 + \ep_2,
	where we used \cref{prop:inner_pd}.
\label{prop:orthog}
	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with length less or equal to $1$,
	which satisfy the condition that 
		H\ket{u} \appd{\ep_1} a \ket{u}, \\
		H\ket{v} \appd{\ep_2} b \ket{v}, 
	for some $a > b \in \R$, then
		\norm{\braket{u}{v}} \leq \frac{\ep_1+\ep_2}{a-b}.
	We write $H\ket{u} = a\ket{u} + \ket{u'}$ such that $\norm{\ket{u'}} \leq \ep_1$.
	Similarly, we write $H\ket{v} = b\ket{v} + \ket{v'}$ such that $\norm{\ket{v'}} \leq \ep_2$.
	Then, we know
		\bra{v}H\ket{u} = a\braket{v}{u} + \braket{v}{u'},\\
		\bra{v}H\ket{u}  =b\braket{v}{u} + \braket{v'}{u},
	Subtracting the second equation from the first equation gives us that 
		\norm{\braket{v}{u}} = \frac{\norm{\braket{v'}{u} -  \braket{v}{u'}}}{a-b} \leq \frac{\norm{\ket{v}}\norm{\ket{u'}}+
		\norm{\ket{u}}\norm{\ket{v'}}}{a-b} 
		\leq \frac{\ep_1+\ep_2}{a-b}.
\label{prop:close_vec}
	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$ and
	$\norm{\ket{v}} \appd{\ep_2} 1$ , if $\braket{u}{v} \geq 1 - \ep_3$,
		\ket{u} \appd{O(\sqrt{\ep_1+\ep_2+\ep_3})} \ket{v}.
\carl{Fix the grammar in the proposition above.}
	Direct calculation gives us that
		\norm{\ket{u} - \ket{v}}^2 &= \norm{\ket{u}}^2 + \norm{\ket{v}}^2 - 2\braket{u}{v} \\
		&\leq (1+\ep_1)^2 + (1+\ep_2)^2 - 2(1 - \ep_3)\\
		&= 2(\ep_1+\ep_2+\ep_3)+ \ep_1^2 + \ep_2^2\\
		& = O(\ep_1+\ep_2+\ep_3).
	Let $\ket{u}$ be a vector with length less than or equal to $1$ such that for a unitary $U$,
		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C,
		U^n \ket{u} \appd{n\ep} a^n \ket{u} \text{ for all } n \geq 1.
	We can prove it by induction. 
	For $n=1$, the statement is satisfied.
	Assume it holds for $n = k-1$ and consider $n = k$, then we have
		&\norm{U^k \ket{u} - a^k\ket{u}} \\
		\leq &\norm{U} \norm{U^{k-1} \ket{\psi} - a^{k-1}\ket{\psi}} + \norm{a^{k-1}}
		\norm{U\ket{\psi} - a \ket{\psi}}\\
		\leq &(k-1)\ep + \ep = k \ep,
	where we used the fact that $\norm{U} = 1$ and $\norm{a} \leq 1$.
